Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-10 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

% Paper title.
\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling a polygonal mesh by
enhancing the object curvature. This method uses an adapted extension
of the Laplace Beltrami operator for hybrid quad/triangle meshes,
to enhance the global curvature. Along with the method, this work
also presents new applications of curvature enhancement in sculpting
and modeling with subdivision surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several modeling techniques have been developed
to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing and creation from sketches \cite{Igarashi1999,Gonen2012},
and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.

Traditional methods for smoothing surfaces from coarse geometry, like
the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
These works generalize the uniform B-cubic splines knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of weights on the vertices to locally control
the zone of influence \cite{Biermann2000}. Instead, the presented
method performs a feature enhancement of the model by parameterizing
the surface curvature and thereby creating a family of different versions
of the same object, preserving therefore the detail of the original
model and a realistic appearance.

@@

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
mesh spectrum from what has been presented so far. The method eliminates
the need of preprocessing and allows preservation of the original
topology. Likewise, along with this operator, it is proposed a method
to generate a family of parameterized shapes, in a robust and predictable
way. This method enables customization of the smoothness and curvature,
obtained during the subdivision surfaces process. Finally, it is proposed
a new brush for enhancing silhouette mesh features in modeling and
sculpting.

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for curvature enhancement and applications of subdivision
of surfaces and sculpting; finally some Laplacian operator results,
to hybrid quad/triangle meshes are graphically shown as well as results
of the curvature enhancement applications in sculpting, subdivision
and modeling.

@@

Many tools have been developed for modeling, based on Laplacian mesh
processing. Thanks to the advantages of the Laplacian operator, these
different tools preserve the surface geometric details when using
them for different processes such as free-form deformation, fusion,
morphing and other application\cite{Sorkine2004}.

Offset polygon mesh methods, based on the curvature defined by the
Laplace Beltrami operator, have been developed. These methods adjust
the shape offset by a constant distance, with high precision as to
minimize the Hausdorf error. Nevertheless, these methods fail to conserve
enough detail because of the smoothing, a crucial issue which depends
on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
representation the computing the offset boundary that are based on
distance field computation, when performing the offset, the topology
of the model may be different from the original, changing the original
design \cite{Chen2011}.

\cite{Gal2009} proposes automatic features detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys with based the first and
second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold. Later the curves are classified by several properties as
planar or non-planar, approximated by lines, circles, ellipses and
other complex shapes. In then the user defines an initial change over
several features and then this change is propagated over other features
with base in the classified shapes and the inter-relationships between
these. This method works fine with objects that have sharp edges composed
of basic geometric shapes such as lines, circles or ellipses but method
has problems to classify when models are smoother with organic forms
because it cannot find the features to edit and preserve.

Digital sculpting can be divided into two principal approaches: based
on polygonal methods and voxel grid-based methods. Brushes for inflate
operations in polygonal methods only depends on the normal at each
vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
allow to add or remove voxels, for produce polygonal meshes require
processing isosurfaces from volume \cite{Galyean1991}. The problem
whit this type of operations is the difficult to maintain surface
details during larger scale deformation.

>>>>

% Paper title.
\title{Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle mesh by
enhancing the global object curvature. This method uses an adapted extension
of the Laplace Beltrami operator. Along with the method, this work
also presents new applications in sculpting
and modeling, with subdivision of surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several modeling techniques have been developed
to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012},
and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.

Traditional methods for smoothing surfaces from coarse geometry, like
the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
These works generalize the uniform B-cubic splines knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of the vertex weights to locally control
the zone of influence \cite{Biermann2000}. Instead, the presented
method performs a feature enhancement of the model by parameterizing
the surface curvature, creating a family of different versions
of the same object and therefore preserving  the detail of the original
model and a more realistic appearance.

@@

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a larger
mesh spectrum from what has been presented so far. The method eliminates
the need of preprocessing and allows preservation of the original
topology. Likewise, along with this operator, it is proposed a method
to generate a family of parameterized shapes, in a robust and predictable
way. This method enables customization of the smoothness and curvature,
obtained during the subdivision surfaces process. Finally, it is proposed
a new brush for enhancing the silhouette mesh features in modeling and
sculpting.

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for curvature enhancement and applications of subdivision
of surfaces and sculpting; finally some Laplacian operator results,
to hybrid quad/triangle meshes are graphically shown as well as results
of the curvature enhancement applications in sculpting, subdivision
and modeling.

@@

Many tools have been developed for modeling, based on the Laplacian mesh
processing. Thanks to the advantages of the Laplacian operator, these
different tools preserve the surface geometric details when using
them for different processes such as free-form deformation, fusion,
morphing and other application\cite{Sorkine2004}.

Offset methods for polygon meshing, based on the curvature defined by the
Laplace Beltrami operator, have been developed. These methods adjust
the shape offset by a constant distance, with enough precision as to
minimize the Hausdorf error. Nevertheless, these methods fail to conserve
sufficient detail because of the smoothing, a crucial issue which depends
on the offset size\cite{Zhuo2012}. In volumetric approaches, in case of point-based
representations, the offset boundary computation is based on the
distance field and therefore when calculating such offset, the topology
of the model may be different to the original  \cite{Chen2011}.

\cite{Gal2009} proposes automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized bytheir first and
second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold.Likewise, curves have been also classified as
planar or non-planar, approximated by lines, circles, ellipses and
other complex shapes. In such case, the user defines an initial change over
several features and this change is propagated towards other features,
based in the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses, but the method
is very limited at classifying when models are smooth since it cannot find the features to edit and preserve.

Digital sculpting have been traditionally approached either under a polygonal representation or a voxel grid-based method. Brushes for inflation operations only depend on the normal vertex \cite{Stanculescu2011}, in grid-based sculpting, some other operations have allowed to add or remove voxels, since producing polygonal meshes require
processing isosurfaces from volume \cite{Galyean1991}. The problem
whit this type of operations is the difficulty of maintaining the surface
details during larger scale deformations.
